formula1: top 9 drivers

### 2020-04-18 inst/formula1.Rmd
more work

see this

>>>>

now profile likelihood:

```{r,doproflikn,cache=TRUE}
H9
maxp(H9)
p <- seq(from=0.11,to=0.13,len=50)
u <- profsupp(H9,"Hamilton",p,n=14)
plot(p,u)
```

# Pole position

We now introduce another reified player, `pole`, whose strength helps
the driver in pole position.

```{r,polepositionlikelihood,cache=TRUE}
HP <- hyper2(pnames=c(rownames(f2017),"pole"))
noscore <- c("Ret", "WD", "DNS", "DSQ", "DNP", "NC")

for(i in seq_len(ncol(f2017))){
	y <- f2017[,i]
	if(any(y %in% noscore)){y[y%in%noscore] <- 0}
	y <- as.numeric(levels(y)[y])
	names(y) <- rownames(f2017)
	HP <- HP + pwa(ordervec2supp(y),details$pole[i],"pole")
} # i loop closes
head(HP)
(mHP <- maxp(HP))
pie(mHP)
```

test Hamilton == bottas:

```{r,dosometests,cache=TRUE}
samep.test(HP,c("Hamilton","Vettel"))
samep.test(HP,c("Hamilton","Bottas"))
```

Now profile likelihood for pole strength:

```{r,profsupcalc,cache=TRUE}
p <- seq(from=0.5,to=0.96,len=20)
pnames(HP)
u <- profsupp(HP,"Ricciardo",p,n=1)
u
plot(p,u-max(u))
```

### 2020-04-18 inst/formula1_points.Rmd
more work

```{r,calcH,cache=TRUE}
H <- hyper2(pnames=rownames(o))
 for(i in seq_len(ncol(o))){
	H <- H + ordervec2supp(o[,i])
}
head(H)
mL2017 <- maxp(H)
mL2017
dotchart(mL2017,pch=16,main='2017 Formula 1')
```

>>>>

```{r,calcH,cache=TRUE}
H <- hyper2(pnames=rownames(o))
 for(i in seq_len(ncol(o))){
	H <- H + ordervec2supp(o[,i])
}
head(H)
mL2017 <- maxp(H)
mL2017
dotchart(mL2017,pch=16,main='2017 Formula 1')
pie(mL2017)
```

### 2020-04-18 inst/formula1_top9.Rmd
change title
more work

---
title: "formula1"
output: html_document
---

@@

## Formula 1

@@

```{r cars}
f2017 <- read.table("formula1_2017.txt",header=TRUE)
f2017a <- f2017[1:9,]
rm(f2017)
f2017a
```

@@

```{r}
f <- function(x){
	noscore <- c("Ret", "WD", "DNS", "DSQ", "DNP", "NC")
	x <- as.character(x)
	x[x %in% noscore] <-  "0"
	x <- as.numeric(x)
	wanted <- x != 0
	xw <- x[wanted]
	xw[order(xw,decreasing=FALSE)] <- seq_along(xw)
	x[wanted] <- xw
	x
}
o  <- apply(f2017a[,seq_len(20)],2,f)
rownames(o) <- rownames(f2017a)
(f2017a <- o)
```

@@

```{r}
wikitable_to_ranktable(f2017a)
```

@@

```{r,hamiltonwetanddry,cache=TRUE}
details <- read.table("formula1_conditions.txt",header=TRUE)
alldrivers <- c("Ham_dry","Ham_wet",rownames(f2017a)[-1])
(L2017 <- hyper2(pnames=alldrivers)) # uninformative
for(i in seq_len(ncol(f2017a))){
	venue <- colnames(f2017a)[i]
	conditions <- details[which(details$venue == venue),4]
	o <- f2017a[,i]
	names(o) <- rownames(f2017a)
	if(conditions == "wet"){
	   names(o)[names(o) == "Hamilton"] <- "Ham_wet"
	} else if(conditions == "dry"){
	   names(o)[names(o) == "Hamilton"] <- "Ham_dry"
	} else {
	   stop("neither wet nor dry?")
	}
	print(o)
	L2017 %<>% order_obs(o)
}  # for(i) loop closes
L2017
```

@@

H <- hyper2(pnames=c(rownames(f2017a),"S"))
noscore <- c("Ret", "WD", "DNS", "DSQ", "DNP", "NC")

for(i in seq_len(ncol(f2017a))){
	y <- f2017a[,i]
	cond <- details$conditions[i]
        jj <- ordervec2supp(y)
	if(cond == "dry"){
            pnames(jj) <- pnames(H)  # do nothing!
	} else if (cond == "wet"){
            jj <- pwa(jj,"Hamilton")
	} else {
            stop("neither wet nor dry?")
	}  # if wet closes
        H <- H + jj
} # i loop closes
head(H)
maxp(H)
```
Now we can test the hypothesis that Hamilton's wet strength `S` is zero:

>>>>

---
title: "formula1: top 9 drivers"
output: html_document
---

@@

## Formula 1: top 9

(this document is largely the same as `formula1.Rmd` but considers
only the top 9 drivers).

@@

```{r cars}
f2017 <- read.table("formula1_2017.txt",header=TRUE)
n <- 9  # top 9
f2017 <- f2017[seq_len(n),]
f2017
```

@@

```{r}
f <- function(x){
	noscore <- c("Ret", "WD", "DNS", "DSQ", "DNP", "NC")
	x <- as.character(x)
	x[x %in% noscore] <-  "0"
	x <- as.numeric(x)
	wanted <- x != 0
	xw <- x[wanted]
	xw[order(xw,decreasing=FALSE)] <- seq_along(xw)
	x[wanted] <- xw
	x
}
o  <- apply(f2017[,seq_len(20)],2,f)
rownames(o) <- rownames(f2017)
(f2017 <- o)
```

@@

```{r}
wikitable_to_ranktable(f2017)
```

@@

```{r,hamiltonwetanddry,cache=TRUE}
details <- read.table("formula1_conditions.txt",header=TRUE)
alldrivers <- c("Ham_dry","Ham_wet",rownames(f2017)[-1])
(L2017 <- hyper2(pnames=alldrivers)) # uninformative
for(i in seq_len(ncol(f2017))){
	venue <- colnames(f2017)[i]
	conditions <- details[which(details$venue == venue),4]
	o <- f2017[,i]
	names(o) <- rownames(f2017)
	if(conditions == "wet"){
	   names(o)[names(o) == "Hamilton"] <- "Ham_wet"
	} else if(conditions == "dry"){
	   names(o)[names(o) == "Hamilton"] <- "Ham_dry"
	} else {
	   stop("neither wet nor dry?")
	}
	print(o)
	L2017 %<>% order_obs(o)
}  # for(i) loop closes
L2017
```

@@

H <- hyper2(pnames=c(rownames(f2017),"S"))
noscore <- c("Ret", "WD", "DNS", "DSQ", "DNP", "NC")

for(i in seq_len(ncol(f2017))){
	y <- f2017[,i]
	cond <- details$conditions[i]
        jj <- ordervec2supp(y)
	if(cond == "dry"){
            pnames(jj) <- pnames(H)  # do nothing!
	} else if (cond == "wet"){
            jj <- pwa(jj,"Hamilton")
	} else {
            stop("neither wet nor dry?")
	}  # if wet closes
        H <- H + jj
} # i loop closes
head(H)
maxp(H)
```
Now we can test the hypothesis that Hamilton's wet strength `S` is zero:
